### 2019-03-30 stableLimit.tex
change stableLimit.tex

%new added
It is know that for any $f\in bp{\cal B}_E$,
\[\label{mean-N}
\mathbb N_{\mu}[W_t(f)]=\mathbf P_{\mu}[X_t(f)]=\mu(P^\beta_tf),
\]
see \cite[Lemma 3.3]{RenSongSun2017Spine} for example. The we see that $\{(X_t(\phi))_{t\geq 0};\mathbf P_{\mu}\}$ is nonnegative martingale,  and $\{(W_t(\phi))_{t\geq 0};\mathbb N_{\mu}\}$ is also a nonnegative martingale.
%end new

@@

\subsection{Characterizing the conditional distribution}
\label{sec: conditional distribution}
	Let $\{X; \mathbf P\}$ be a superprocess satisfies
	$Assumption \ref{asp: 1}, \ref{asp: 2}, \ref{asp: 3} and \ref{asp: 4}.
	Assumptions \ref{asp: 1}-\ref{asp: 4}.
	Suppose that $m(x: \gamma(x) = \gamma_0)>0$.
	Recall that we want to find a proper normalization $(\eta_t)_{t\geq 0}$ such that $\big\{\big(\eta_t X_t(f))_{t \geq 0}; \mathbf P_\mu(\cdot | X_t \not \equiv 0\big)\big\}$
	%convergence weakly 
	converges weakly
	to a non-degenerate distribution for a large class of testing function $f$ and initial configuration $\mu$.
	Our guess of $(\eta_t)$ is
\[
	\eta_t
	:= (C_X(\gamma_0 - 1) t)^{-\frac{1}{\gamma_0 - 1}},
	\quad t\geq 0,
\]
	because in this case $\big\{\big(\eta_t X_t(f)\big)_{t \geq 0}; \mathbf P_{\delta_x}(\cdot | X_t \not \equiv 0)\big\}$ have the mean convergence:
 \[
 	\mathbf P_{\delta_x}[\eta_t X_t(f)|X_t \not \equiv 0]
	= \frac{\mathbf P_{\delta_x}[\eta_t X_t(f) \mathbf 1_{X_t \not \equiv 0}]} {\mathbf P_{\delta_x}(X_t \not \equiv 0) }
	= \frac{\eta_t}{\mathbf P_{\delta_x}(X_t \not \equiv 0)} P^\beta_t f(x)
	\stackrel[t\to \infty]{}{\sim}  \langle f,\phi^* \rangle_m.
 \]
 	Here we have used Theorem \ref{thm: main theorem}(2) and the fact that (see \eqref{eq:q(t,x,y)})
 \[
 	P^\beta_t f(x)
 	= \int_E p_t^\beta(x,y)f(y)dy
 	\xrightarrow[t\to \infty]{}  \phi(x) \langle f,\phi^*\rangle_m.
 \]

>>>>

%new added
It is know that for any $f\in bp\mathcal{B}_E$,
\[\label{mean-N}
\mathbb N_{\mu}[W_t(f)]=\mathbf P_{\mu}[X_t(f)]=\mu(P^\beta_tf),
\]
see \cite[Lemma 3.3]{RenSongSun2017Spine} for example. The we see that $\{(X_t(\phi))_{t\geq 0};\mathbf P_{\mu}\}$ is nonnegative martingale,  and $\{(W_t(\phi))_{t\geq 0};\mathbb N_{\mu}\}$ is also a nonnegative martingale.
%end new

@@

\subsection{Characterizing the conditional distribution}
\label{sec: conditional distribution}
	Let $\{X; \mathbf P\}$ be a superprocess satisfies
	%Assumption \ref{asp: 1}, \ref{asp: 2}, \ref{asp: 3} and \ref{asp: 4}.
	Assumptions \ref{asp: 1}-\ref{asp: 4}.
	Suppose that $m(x: \gamma(x) = \gamma_0)>0$.
	Recall that we want to find a proper normalization $(\eta_t)_{t\geq 0}$ such that $\big\{\big(\eta_t X_t(f))_{t \geq 0}; \mathbf P_\mu(\cdot | X_t \not \equiv 0\big)\big\}$
	%convergence weakly
	converges weakly
	to a non-degenerate distribution for a large class of testing function $f$ and initial configuration $\mu$.
	Our guess of $(\eta_t)$ is
\[
	\eta_t
	:= (C_X(\gamma_0 - 1) t)^{-\frac{1}{\gamma_0 - 1}},
	\quad t\geq 0,
\]
	because in this case $\big\{\big(\eta_t X_t(f)\big)_{t \geq 0}; \mathbf P_{\delta_x}(\cdot | X_t \not \equiv 0)\big\}$ have the mean convergence:
 \[
 	\mathbf P_{\delta_x}[\eta_t X_t(f)|X_t \not \equiv 0]
	= \frac{\mathbf P_{\delta_x}[\eta_t X_t(f) \mathbf 1_{X_t \not \equiv 0}]} {\mathbf P_{\delta_x}(X_t \not \equiv 0) }
	= \frac{\eta_t}{\mathbf P_{\delta_x}(X_t \not \equiv 0)} P^\beta_t f(x)
	\stackrel[t\to \infty]{}{\sim}  \langle f,\phi^* \rangle_m.
 \]
 	Here we have used Theorem \ref{thm: main theorem}(2) and the fact that (see \eqref{eq:q(t,x,y)})
 \[
 	P^\beta_t f(x)
 	= \int_E p_t^\beta(x,y)f(y)dy
 	\xrightarrow[t\to \infty]{}  \phi(x) \langle f,\phi^*\rangle_m.
 \]
